My Linux Notes

### 2018-07-23 Ubuntu_16.04_setup/mylinux.Rmd
up

---
title: "My Linux Notes"
subtitle: "A Quick Reference"
author: "[Yongfu Liao](https://liao961120.github.io/)"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
link-citations: yes
output:
  bookdown::html_document2:
    css: /home/liao/local_depend/style_sheets/style.css
    df_print: kable
    toc: true
    toc_depth: 2
    toc_float:
        collapsed: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE,
	dev='svg',
	fig.dim = c(5.5, 3.5)  # (width, height)
)
```

@@

```bash
cat ~/foo.txt >> doc.Rmd
echo "!!" >> file.txt
```

Then the command appends literal `cat ~/foo.txt >> doc.Rmd
echo "!!" >> file.txt` to the end of `file.txt`.

@@

Original files in the working dir:
```
dir2/
01-file.txt
02-file.txt
.
.
41-file.txt
README.md
```

```bash
for i in {01..41}
do 
	mv $(echo $i'*') $(echo $i'.txt')
done
```

After executing the code above:
```
dir2/
01.txt
02.txt
.
.
41.txt
README.md
```

@@

e.g.
```bash
ln -s $(pwd)/blah.txt ~/Desktop/blah-sym
```

@@

> Port 22
> PasswordAuthentication yes
> PermitRootLogin yes

>>>>

---
title: "My Linux Notes"
subtitle: "A Quick Reference"
author: "[Yongfu Liao](https://liao961120.github.io/)"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
link-citations: yes
output:
  bookdown::html_document2:
    highlight: haddock
    css: /home/liao/local_depend/style_sheets/style.css
    df_print: kable
    toc: true
    toc_depth: 2
    toc_float:
        collapsed: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE,
	comment = ">",
	dev='svg',
	fig.dim = c(5.5, 3.5)  # (width, height)
)
```

@@

```bash
cat ~/bash_pract/rmd-head.txt >> ~/bash_pract/doc.Rmd
echo "!!" >> ~/bash_pract/cmd_hist
```

Then the command appends literal `cat ~/bash_pract/rmd-head.txt >> ~/bash_pract/doc.Rmd` to the end of `cmd_hist`. Note that this **works only on the command line**, not shell scripts.

@@

```{bash, preprocess-dir, include=FALSE}
cd ~/bash_pract && rm -r dir
mkdir dir dir/dir2
touch dir/{01..03}-file.txt dir/README
```

Original files in the working dir:
```{bash}
ls ~/bash_pract/dir
```

Then, running the code below:
```{bash}
cd ~/bash_pract/dir

for i in {01..03}; do 
	mv $(echo $i'*') $(echo $i'.txt')
done

ls
```

@@

e.g.
```{bash}
cd ~/bash_pract
echo "Before:
$(ls -l)"

ln -s $(pwd)/dir/foo.txt $(pwd)/foo-sym

echo "
After:
$(ls -l)"
```

```{bash include=FALSE}
rm ~/bash_pract/foo-sym
```

@@

> Port 22
>
> PasswordAuthentication yes
>
> PermitRootLogin yes
